---
title: "greatR — full pipeline example"
output: html_document
---

This document runs the same logical steps as the vignettes (**read sample data → `register()` → summaries and plots**), but without relying on a precomputed `readRDS()` registration object. Use it to smoke-test the package after changes.

```{r setup, message=FALSE}
# From a package checkout (this repo), load the in-development sources.
# From an installed package only, `library(greatR)` is enough.
if (file.exists("R/distance.R") && requireNamespace("pkgload", quietly = TRUE)) {
  pkgload::load_all(quiet = TRUE)
}
library(greatR)
library(data.table)
```

## Read data

```{r read}
path_csv <- system.file("extdata/brapa_arabidopsis_data.csv", package = "greatR")
stopifnot(path_csv != "")
b_rapa_data <- fread(path_csv)
head(b_rapa_data)
```

## Register

Same call as `vignettes/register-data.Rmd`, except optimisation is limited here so this document knits in reasonable time. For publication-quality optimisation, omit `optimisation_config` (defaults are higher).

```{r register, message=FALSE, warning=FALSE}
registration_results <- register(
  b_rapa_data,
  reference = "Ro18",
  query = "Col0",
  scaling_method = "z-score",
  optimisation_config = list(num_iterations = 30, num_fun_evals = 30)
)

registration_results$model_comparison
```

## Summarise and plot registration

```{r summary-plot, fig.height=4, fig.width=4.5}
reg_summary <- summary(registration_results)
reg_summary$summary
plot(reg_summary, type = "registered", scatterplot_size = c(4, 3.5))
```

```{r plot-curves, fig.height=8, fig.width=7, warning=FALSE}
plot(registration_results, ncol = 2)
```

## Distances and heatmaps

```{r distance, message=FALSE}
sample_distance <- calculate_distance(registration_results)
```

```{r plot-dist, fig.height=4, fig.width=7, warning=FALSE}
plot(sample_distance, type = "original")
plot(sample_distance, type = "result", match_timepoints = TRUE)
```
